Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-03-27 additional_files/main_text.tex
Pass text through aspell and correct a few other mistakes; manuscript considered ready, version sent to co-authors for approval
Add README and LICENSE; add reference to Tuteja and Vodkin (2008)'s contig and SoySNP50K data in manuscript

\subsection*{Loci with known genes or causal mutations}
\label{sv-gwas-results-cloned-genes}

@@

The two known loci for pubescence form in soybean, \textit{Pa1} and
\textit{Pa2}, have also not been cloned yet. Nevertheless, \cite{gilbert2017}
has suggested Glyma.12g213900 as a candidate for \textit{Pa1} based on data
published by \cite{bandillo2017}. This gene encodes a Myb transcription factor
annotated as playing a role in trichome branching. Indeed, the most significant
signals found by all three approaches were located near this gene (Figure
\ref{pubescence-form-main-figure}a-b, and Additional file 1: Figures \ref{pubescence_form_all_manhattan} and
\ref{pubescence_form_all_Pa1_signal}).  The analyses based on SNPs and
\emph{k}-mers identified two highly significant non-synonymous SNPs in
Glyma.12g213900 that were associated with appressed pubescence (Figure
\ref{pubescence-form-main-figure}c-d and Additional file 1: Figures \ref{pubescence_form_all_Pa1_gene} and
\ref{pubescence_form_all_Pa1_kmers}). The alternative alleles for these two
SNPs co-occurred together in our dataset and may represent causal variants at
the \emph{Pa1} locus. The signals observed at the \emph{Pa2} locus were much
weaker and the signal observed from the \emph{k}-mer GWAS overlapped a total of
20 genes (Additional file 1: Figures \ref{pubescence_form_all_manhattan} and
\ref{pubescence_form_all_Pa2_signal}), none of which appeared obviously linked
to pubescence form.

@@

>>>>

\subsection*{Loci with known genes or causal variants}
\label{sv-gwas-results-cloned-genes}

@@

The two known loci for pubescence form in soybean, \textit{Pa1} and
\textit{Pa2}, have also not been cloned yet. Nevertheless, \cite{gilbert2017}
has suggested Glyma.12g213900 as a candidate for \textit{Pa1} based on data
published by \cite{bandillo2017}. This gene encodes a MYB transcription factor
annotated as playing a role in trichome branching. Indeed, the most significant
signals found by all three approaches were located near this gene (Figure
\ref{pubescence-form-main-figure}a-b, and Additional file 1: Figures \ref{pubescence_form_all_manhattan} and
\ref{pubescence_form_all_Pa1_signal}).  The analyses based on SNPs and
\emph{k}-mers identified two highly significant non-synonymous SNPs in
Glyma.12g213900 that were associated with appressed pubescence (Figure
\ref{pubescence-form-main-figure}c-d and Additional file 1: Figures \ref{pubescence_form_all_Pa1_gene} and
\ref{pubescence_form_all_Pa1_kmers}). The alternative alleles for these two
SNPs co-occurred together in our dataset and may represent causal variants at
the \emph{Pa1} locus. The signals observed at the \emph{Pa2} locus were much
weaker and the signal observed from the \emph{k}-mer GWAS overlapped a total of
20 genes (Additional file 1: Figures \ref{pubescence_form_all_manhattan} and
\ref{pubescence_form_all_Pa2_signal}), none of which appeared obviously linked
to pubescence form.

@@

The \textit{I} locus contig assembled by \cite{tuteja2008} is available from
NCBI (\url{https://www.ncbi.nlm.nih.gov/nuccore/EF623854}).

SoySNP50K genotype calls are available from SoyBase (\url{https://soybase.org/snps/}).
